Adversarial Training against Systematic Uncertainty

### 2016-09-02 tex/paper.tex
savce

\title{Adversarial Training of Neural Networks\\
against Systematic Uncertainty}

% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
  Gilles Louppe \\
  New York University\\
  \texttt{g.louppe@nyu.edu} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  %% \texttt{email} \\
}

@@

\begin{abstract}
\end{abstract}

@@

\begin{algorithm}
\caption{Adversarial training of a classifier $f$ against an adversary $r$.\\
{\it Inputs:} training data $\{ x_i, y_i, z_i \}_{i=1}^N$\\
{\it Outputs:} $\smash{\hat\theta_f}, \smash{\hat\theta_r}$\\
{\it Hyper-parameters:} Number $T$ of training iterations, Number $K$ of gradient steps to update $r$.}
\label{alg:adversarial-training}
\begin{algorithmic}[1]
    \For{$t=1$ to $T$}
        \For{$k=1$ to $K$} \Comment{Update $r$}
            \State{Sample minibatch $\{x_m, z_m \}_{m=1}^M$} of size $M$;
            \State{With $\theta_f$ fixed, update $r$ by ascending its stochastic gradient $\nabla_{\theta_r} E(\theta_f, \theta_r) :=$
            $$\nabla_{\theta_r} \sum_{m=1}^M \left[\sum_{z_l \in {\cal Z}} 1(z_m = z_l)\log r(f(x_m;\theta_f);\theta_r)_l \right];$$}
        \EndFor
        \State{Sample minibatch $\{x_m, y_m, z_m \}_{m=1}^M$} of size $M$; \Comment{Update $f$}
        \State{With $\theta_r$ fixed, update $f$ by descending its stochastic gradient $\nabla_{\theta_f} E(\theta_f, \theta_r) :=$
        $$\nabla_{\theta_f}  \sum_{m=1}^M \left[ -\sum_{y_c \in {\cal Y}} 1(y_m = y_c) \log f(x_m;\theta_f)_c  +\sum_{z_l \in {\cal Z}} 1(z_m = z_l)\log r(f(x_m;\theta_f);\theta_r)_l \right];$$}
    \EndFor
\end{algorithmic}
\end{algorithm}

\glnote{Extension to continuous nuisance parameters: have the adversary $r$
models the conditional distribution $p(z|f(X;\theta_f))$, e.g. with a network
whose 2 outputs are the parameters of a truncated gaussian and optimized such that
$p(z|f(X;\theta_f)) \approx N(\mu(f(X;\theta_f);\theta_r), \sigma(f(X;\theta_f);
\theta_r)$. The associated loss can be the likelihood (or?), which is maximal when the
approximation is perfect and minimal when the truncated gaussian degenerates to
a uniform (when $\sigma$ is large), in which case we should have the guarantee
that $f$ is pivotal.}

@@

\glnote{This seems to naturally extend to the case where $Z$ takes continuous
value, where $L_r$ could be a continuous version of the cross-entropy?}

>>>>

\title{Adversarial Training against Systematic Uncertainty}

\author{
  Gilles Louppe \\
  New York University\\
  \texttt{g.louppe@nyu.edu} \\
  \And
  Michael Kagan\\
  SLAC National Accelerator Laboratory\\
  \texttt{makagan@slac.stanford.edu}\\
  \And
  Kyle Cranmer \\
  New York University\\
  \texttt{kyle.cranmer@nyu.edu}
}

@@

\begin{abstract}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Donec in faucibus
lacus. Curabitur in viverra neque. Sed nec urna a sem blandit viverra vel a
eros. Nam a ultrices leo, a aliquet diam. Proin cursus scelerisque leo, ut
ullamcorper ante auctor et. Nulla odio nisl, molestie eget consectetur quis,
eleifend id ligula. Cras lobortis egestas justo ac sagittis. In at ligula est.
Nulla vel eros sapien. Sed bibendum metus quis dignissim scelerisque. Nulla arcu
lectus, ornare nec vehicula quis, lobortis a mi. Cras scelerisque mauris quam,
nec viverra ex convallis sit amet. Ut tellus turpis, lobortis sit amet finibus
sit amet, maximus ac est.

\end{abstract}

@@

\begin{algorithm}[t]
\caption{Adversarial training of a classifier $f$ against an adversary $r$.\\
{\it Inputs:} training data $\{ x_i, y_i, z_i \}_{i=1}^N$\\
{\it Outputs:} $\smash{\hat\theta_f}, \smash{\hat\theta_r}$\\
{\it Hyper-parameters:} Number $T$ of training iterations, Number $K$ of gradient steps to update $r$.}
\label{alg:adversarial-training}
\begin{algorithmic}[1]
    \For{$t=1$ to $T$}
        \For{$k=1$ to $K$} \Comment{Update $r$}
            \State{Sample minibatch $\{x_m, z_m \}_{m=1}^M$} of size $M$;
            \State{With $\theta_f$ fixed, update $r$ by ascending its stochastic gradient $\nabla_{\theta_r} E(\theta_f, \theta_r) :=$
            $$\nabla_{\theta_r} \sum_{m=1}^M \left[\sum_{z_l \in {\cal Z}} 1(z_m = z_l)\log r(f(x_m;\theta_f);\theta_r)_l \right];$$}
        \EndFor
        \State{Sample minibatch $\{x_m, y_m, z_m \}_{m=1}^M$} of size $M$; \Comment{Update $f$}
        \State{With $\theta_r$ fixed, update $f$ by descending its stochastic gradient $\nabla_{\theta_f} E(\theta_f, \theta_r) :=$
        $$\nabla_{\theta_f}  \sum_{m=1}^M \left[ -\sum_{y_c \in {\cal Y}} 1(y_m = y_c) \log f(x_m;\theta_f)_c  +\sum_{z_l \in {\cal Z}} 1(z_m = z_l)\log r(f(x_m;\theta_f);\theta_r)_l \right];$$}
    \EndFor
\end{algorithmic}
\end{algorithm}

\glnote{Extension to continuous nuisance parameters: have the adversary $r$
models the conditional distribution $p(z|f(X;\theta_f))$, e.g. with a network
whose 2 outputs are the parameters of a truncated gaussian and optimized such that
$p(z|f(X;\theta_f)) \approx N(\mu(f(X;\theta_f);\theta_r), \sigma(f(X;\theta_f);
\theta_r)$. The associated loss should be the negative log-likelihood (= cross-entropy), which is maximal when the
approximation is perfect and minimal when the truncated gaussian degenerates to
a uniform (when $\sigma$ is large), in which case we should have the guarantee
that $f$ is pivotal.}

\glnote{This section and theoretical results should be rewritten in such a way
that categorical and continuous nuisance values are solved under the same
principled approach.}

@@
